Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
Figure 2 is ready

movratedf %>% 
  ggplot(., aes(x = movrate, y = factor(scenario, levels = c("pp", "np", "cp")), color = as.character(group))) +
  geom_point(size = 3, alpha = 0.8) +
  scale_color_manual(values = cols.fig2) +
  scale_x_continuous(limits = c(0, 70)) +
  labs(x = "Movement Rate (meters/minute)", y = "Model scenario",
       title = "Sampled movement rates for each simulated scenario") +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  #theme(legend.position = "none") +
  NULL-> movrates_used

>>>>

movratedf %>% 
  ggplot(., aes(x = movrate, y = factor(scenario, levels = c("pp", "np", "cp")), color = as.character(group))) +
  geom_jitter(size = 3, alpha = 0.8, height = 0.1) +
  scale_color_manual(values = cols.fig2) +
  scale_x_continuous(limits = c(0, 70)) +
  labs(x = "Movement Rate (meters/minute)", y = "Model scenario",
       title = "Sampled movement rates for each simulated scenario") +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  #theme(legend.position = "none") +
  NULL-> movrates_used

movrates_used
